---
title: "Mileage per Gallon Predictor"
author: "Sanket Bambodkar"
date: "14 June 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Application Summary

This application predicts mileage per gallon of your car based on some specifications such as horsepower, number of cylinders and gear transmission mode.    
The prediction model in based upon **mtcars** dataset in R

```{r echo = FALSE, error = FALSE, comment=""}
head(mtcars)
```

Source Code:
[Github](http://github.com/gomugomu0034/Shiny-App)

Application:
[ShinyApp](https://sanketbambodkar.shinyapps.io/mpgpredictor/)

## How It Works
- The application is written in **Shiny** which is a web application framework for R   
- The source code consists of two files: server.R and ui.R    
- **server.R** includes the the server logic of a Shiny web application   
- **ui.R** includes the the user-interface definition, which uses the sidebarLayout template    
- The application is hosted on Rstudio's shiny server in the cloud (**Shinyapps.io**)  

## Model Design
Models are based on **mtcars** dataset in R   
**Model 1** is a simplistic model with mileage per gallon as the outcome and horsepower as the predictor.    
**Model 2** is a multivariable model which uses horsepower, number of cylinders and geat transmission mode as the predictors.   

```{r eval=FALSE, error=FALSE, echo=TRUE, fig.align='center'}
model1 <- lm(mpg ~ hp, data = mtcars)
model2 <- lm(mpg ~ hp + factor(cyl) + factor(am), data = mtcars)
hpInput <- input$hp
if(input$am == "Automatic") {amInput <- 1} else {amInput <- 0}
cylInput <- input$cyl
model1pred <- reactive({
          predict(model1, newdata = data.frame(hp = hpInput))})
model2pred <- reactive({
predict(model2, newdata = data.frame(hp = hpInput, 
        cyl = cylInput, am = amInput))})
```

## Prediction Outpuut
This is a graph between mileage per gallon (y axis) vs horsepower (x axis).   
Red line denotes model 1 and blue line denotes model 2.    
```{r eval=TRUE, error=FALSE, echo=FALSE, fig.align='center', warning=FALSE}
model1 <- lm(mpg ~ hp, data = mtcars)
model2 <- lm(mpg ~ hp + factor(cyl) + factor(am), data = mtcars)
hpInput <- 200
amInput <- 1
cylInput <- 6
model1pred <- predict(model1, newdata = data.frame(hp = hpInput))
model2pred <- predict(model2, newdata = data.frame(hp = hpInput, 
        cyl = cylInput, am = amInput))
plot(mtcars$hp, mtcars$mpg, xlab = "Horsepower", ylab = "Miles per Gallon",
        pch = 16, xlim = c(50,350), ylim = c(10,35)) +
abline(model1,col = "red", lwd = 2)+
abline(model2, col = "blue", lwd = 2)+
points(hpInput, model1pred, col = "red", pch = 20, cex = 2)+
points(hpInput, model2pred, col = "blue", pch = 20, cex = 2)
```
